---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `{rpt}` ([R]{.underline} [p]{.underline}ackage [t]{.underline}emplate)


<!-- badges: start -->
[![R-CMD-check](https://github.com/UCD-SERG/rpt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UCD-SERG/rpt/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/UCD-SERG/rpt/graph/badge.svg)](https://app.codecov.io/gh/UCD-SERG/rpt)
[![CodeFactor](https://www.codefactor.io/repository/github/ucd-serg/rpt/badge)](https://www.codefactor.io/repository/github/ucd-serg/rpt)
[![CRAN status](https://www.r-pkg.org/badges/version/rpt)](https://CRAN.R-project.org/package=rpt)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{rpt}` is to ...

## Installation

You can install the development version of `{rpt}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("UCD-SERG/rpt")
```

## Setup

After cloning this template, make sure your GitHub Pages settings at `https://github.com/UCD-SERG/[PACKAGE-NAME]/settings/pages` are configured to deploy from the `docs/` folder on the `gh-pages` branch.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rpt)
## basic example code
```

## Other R Package Template Options

If you're looking for alternative R package templates, you may also want to consider:

- [r.pkg.template](https://github.com/insightsengineering/r.pkg.template/) - A comprehensive R package template from Insights Engineering

## Code of Conduct

Please note that the `{rpt}` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
